---
title: "assignment_1"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```


# call built-in data mtcars.
```{r}
data(mtcars)
```

# Select only car models where mpg<20
```{r}
mtcars_mpg2 <- mtcars[mtcars$mpg < 20,]
```

# Reduce the variables to mpg, cyl, disp, hp, gears
```{r}
mtcars_mpg2 <- mtcars_mpg2[, c(1,2,3,4,10)]
```

# read the R file hand_functions.R so that it can be used
# notice that with echo = TRUE 
```{r}
source(file = "~/Downloads/hand_functions.R", echo = TRUE)
```

# Now use the function from hand_functions.R
```{r}
sp_out <- sum_special(mtcars_mpg2)
```

# library(esquisse)
# 
# esquisser(data = mtcars_mpg2, viewer = "browser")

```{r}
ggplot(mtcars_mpg2) +
  aes(x = disp, y = mpg) +
  geom_point(shape = "bullet", size = 4L, colour = "#B22222") +
  geom_smooth(span = 0.5) +
  theme_minimal()
```

# note that this boxplot cannot be made with esquisse() unless
# the data is adjusted.  What adjustment is needed?

```{r}
ggplot(mtcars_mpg2, aes(x=as.factor(cyl), y=mpg)) + 
  geom_boxplot(fill="slateblue", alpha=0.2) + 
  xlab("cyl")
```


x=as.factor(cyl) should change to equal a categorical value, first I will creat a value cyl = as.factor(mtcars_mpg$cyl), then change x=as.factor(cyl) as x= cyl.



